A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2023-01-09 kobakian-cook.Rmd
small changes to code

tas_ggcont <- ggplot(cont) + 
  geom_sf(fill = "#D3D3D3", colour = "white", data = sa2thyroid_ERP) +
  geom_sf(aes(fill = SIR), colour = "grey", size = 0.01) + 
  scale_fill_identity() + guides(fill = "none") +
  theme_map()
#tas_ggcont
```

>>>>

tas_ggcont <- ggplot(cont) + 
  geom_sf(fill = "#D3D3D3", colour = "white", data = sa2thyroid_ERP) +
  geom_sf(aes(fill = SIR), colour = "grey", size = 0.01) + 
  scale_fill_identity() + guides(fill = "none") +
  theme_map()
```
